A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-31 tidyindex.qmd
Update Intro paragraph 1

Indexes are commonly used to combine multivariate information into a single number for monitoring, communicating, and decision-making across various domains in society. Their applications can be found in the environment (e.g. Air Quality Index, El Niño-Southern Oscillation Index), in the economy (Consumer Price Index, stock market indexes), and in the social sciences (e.g. QS University Rankings, Human Development Index).

>>>>

Indexes are commonly used to combine and summarize different sources of information into a single number for monitoring, communicating, and decision-making. Examples of those include the Air Quality Index, El Niño-Southern Oscillation Index, Consumer Price Index, QS University Rankings or Human Development Index among many others.
